How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-11 paper.tex
more text

\subsection{Try to solve your own problem}

@@

GitHub issue templates \cite{github-templates}

@@

Alan Grossfield serves as a consultant to two companies, Moderna Therapeutics
and Atelerix Life Sciences.

>>>>

\subsection{Try to solve your own problem}
\label{ss:yourself}

@@

The next step in the process is to actually communicate your issue with the
developers, generally in the form of a bug report.  Doing so effectively
requires striving for two somewhat contradictory goals: you must give the
developer all of the relevant information about the problem, as concisely as
possible.

Taking the first part first: this is hard, because as a user you're usually not
an expert, \emph{so you don't know what's relevant}. The only way to know for
sure what is and isn't relevant is to develop a mental model for the problem,
which requires effort. Still, as pointed out above, your prior efforts to solve
the problem yourself (see \ref{ss:yourself}) will help you here.  Moreover, you
may find that the act of writing the note asking for help may in itself let you
solve your problem. The process is analogous to rubber duck debugging
\cite{Thomas-1999}, in that the act of figuring out how to describe a problem
clearly can lead you to a solution.

Moreover, many developers will help you with the process. For example,
GitHub-based projects have the option to set up issue templates
\cite{github-templates}; as the name implies, these templates contain a series
of questions one should answer when submitting a new issue. Although they are
generally customized for each project, these questions are also a good baseline
for the kinds of information one should supply when asking for support
elsewhere. For example, for a bug report one should

\begin{itemize}

    \item Describe the bug, including the expected behavior and how the current
    behavior differs.

    \item Give steps necessary to reproduce the bug.

    \item Describe the platform you're running on (e.g. the operating system for
    a conventional computer, hardware if it's a tablet, etc.). If the problem is
    related to building or installing the software, describe the build system
    (e.g. compiler version) or package manager (e.g. Conda\cite{ANACONDA}).

\end{itemize}

For a feature request, you would also describe what you hope to accomplish and
how you'd like to see it work, as well as any current workaround you've
developed.

@@

Alan Grossfield serves as a consultant to two companies, Moderna, Inc.
and Atelerix Life Sciences.
